Figures

### 2019-05-02 figures/07_model-selection.Rmd
towards crude caching of model fits

# linear
model_form <- bf(tp ~ agvpct)
fit0 <- brm(formula = model_form, data = dt, 
           family = gaussian())

>>>>

brm_fit <- function(destfile, formula, data){
  fit <- brm(formula = formula, data = data, 
           family = gaussian())
  saveRDS(fit, destfile)
  return(fit)
}

# linear
model_form <- bf(tp ~ agvpct)
fit0 <- get_if_not_exists(brm_fit, "fit0.rds", formula = model_form, data = dt)
